### 2020-03-03 submission/manuscript.Rmd
Emphasize 2 different abilities (generating, analzying)

For most biologists, the ability to generate data has outpaced the ability to analyze those data. High throughput data comes to us from DNA and RNA sequencing, flow cytometry, metabolomics, molecular screens, and more. Although some accept the approach of compartmentalizing the ability to generate data and analyze data, we have found scientists feel empowered when they have the ability to both ask and answer their own biological questions. Yet, the standard undergraduate and graduate training in the biological sciences is insufficient to develop the data analysis skills needed to analyze one's data. In our experience performing microbiome research, it is more common to find exceptional bench scientists who are inexperienced at analyzing large datasets than to find the reverse. Of course this raises a challenge: How do we train bench scientists to analyze datasets to answer biological questions?

>>>>

For most biologists, the ability to generate data has outpaced the ability to analyze those data. High throughput data comes to us from DNA and RNA sequencing, flow cytometry, metabolomics, molecular screens, and more. Although some accept the approach of compartmentalizing the ability to generate data and the ability analyze data, we have found scientists feel empowered when they can both ask and answer their own biological questions. Yet, the standard undergraduate and graduate training in the biological sciences is insufficient to develop the data analysis skills needed to analyze one's data. In our experience performing microbiome research, it is more common to find exceptional bench scientists who are inexperienced at analyzing large datasets than to find the reverse. Of course this raises a challenge: How do we train bench scientists to analyze datasets to answer biological questions?
